### 2018-07-19 manuscript.tex
Update manuscript.tex

We conceptualized the main constrcuts in testing the three theories of FGC practice aformentioned based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}. (to confirm and update) The heory of planned behavior proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

@@

The main response variables were woman's opinion (or attitude?) on whether they think FGC should be continued in the FGC future model and woman's intention of cut their daughters in the daughter's FGC status model.  The main predictors in both of the models were beliefs of FGC benefits (see the list of FGC benefits at table-- in Appendix) and woman's FGC status.  We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.  It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.  We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.

>>>>

The main constrcuts of analyzing FGC practice in this study were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92}. (to confirm and update) The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, media use and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

@@

The main response variables were woman's attitude on whether they think FGC should be continued in the FGC future model and woman's intention of cutting their daughters in the daughter's FGC status model.  The main predictors in both of the models were attitudes of FGC benefits and woman's FGC status.  We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.  It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.  We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.
